Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-24 VMCAI-revised-version/final.tex
up
effectivity

@@

$\post$-effective, $\post$-ideal-effective WSTS, strong downward compatibility and upward compatibility include for instance
Lossy Channel Systems with insertions~\cite{DBLP:journals/iandc/AbdullaJ96, DBLP:journals/iandc/CeceFI96}.

@@

\alain{remercier les reviewers !}

>>>>

	\vspace{-1.2cm}

@@

$\post$-effective, $\post$-ideal-effective WSTS, strong downward compatibility and upward compatibility include for instance
Lossy Channel Systems with insertions~\cite{DBLP:journals/iandc/AbdullaJ96,DBLP:journals/iandc/CeceFI96}.

@@

\alain{remercier les reviewers !} We thank the reviewers of the VMCAI 2024 conference for their numerous and relevant comments and improvement suggestions.
